fGFPCA dynamic prediction (In-sample)

### 2023-01-02 f-GFPCA.Rmd
add GLMM intercept function

---
title: "fGFPCA dynamic prediction (In-sample)"
output: 
  html_document:
    toc: true
    toc_float: true
    toc_depth: 3
date: "2022-11-03"
---

@@

@@

Now let's say if we have a new subject with observations up to $t_m$ and $t_m$ is in mth bin:

@@

>>>>

---
title: "fGFPCA dynamic prediction (In-sample)"
output: 
  html_document:
    toc: true
    toc_float: 
      collapsed: false
    toc_depth: 3
date: "2022-11-03"
---

@@

Figure below is the "mean" latent function across subject, which essential is $\beta_0^s$ from the series of mixed models.

```{r,fig.height=4, fig.width=4}
ggplot(data.frame(x=mid, y=mean_latent))+
  geom_line(aes(x=x, y=y))
```

@@

Now let's say if we have a new subject $\boldsymbol{Y}_{new}$ with observations up to $t_m$ and $t_m$ is in mth bin. Also, we do not wish to refit any model, including the local GLMMs. In the first step, we need to use the series of local GLMMs that's already been fitted to get the random intercepts for this new observations ($\boldsymbol{b}_{new}$).

We first focus on one specific interval s.

@@

```{r}
```
